---
title: "Challenge-6"
author: "Alicia Tan"
date: "`20 Sept 2023`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Output preview:** Here is how the countdown could look like 

```


**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here

rocket_countdown <- function() {
  countdown <- 10
  
  while (countdown >= 1) {
    cat(countdown, "...")
    Sys.sleep(1)  
    countdown <- countdown - 1
  }
  
  cat("Blastoff!\n")
}

rocket_countdown()

```
<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=TRUE,echo=TRUE}
# Enter code here

reverse_word <- function() {
  word <- readline("Enter a word: ")
  length_word <- nchar(word)
  reversed_word <- ""
  
  while (length_word > 0) {
    reversed_word <- paste(reversed_word, substr(word, length_word, length_word), sep = "")
    length_word <- length_word - 1
  }
  
  cat("Reversed word:", reversed_word, "\n")
}

reverse_word()


```
<br>
